Quality Definitions of Qualities

### 2020-01-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated performance, maintainability, portability and made comments in regrads to McCall

\begin{defn} \label{PerformanceDefnSelected}
	The degree to which a system or component accomplishes its designated functions
	within given constraints, such as speed, accuracy, or memory usage
	\citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn} \label{PerformanceDefnSelected2}
	How well or how rapidly the system must perform specific functions. Performance
	requirements encompass speed (database response times, for instance), throughput
	( transactions per second), capacity (con-current usage loads), and timing (hard
	real-time demands) \citep{wiegers2003softreq}.
\end{defn}
\begin{defn}
	In software engineering we often equate performance with efficiency. A software
	system is efficient if it uses computing resources economically
	\citep{ghezzi1991fundamentals}.
\end{defn}

@@

Combined definition \ref{PerformanceDefnSelected} and
\ref{PerformanceDefnSelected2}: The degree to which a system or component
accomplishes its designated functions within given constraints, such as speed
(database response times, for instance), throughput (transactions per second),
capacity (con-current usage loads), and timing (hard real-time
demands). \wss{What is the difference between speed and timing?}

@@

\pmi{I will check if Wiegers discusses the difference between speed and timing.}
\pmi{Wiegers did not discuss this difference.}
\pmi{Speed - change over time; timing - related to specification: when something
	should happen in relation to something else - state transitions}
\wss{If we need both speed and timing, we should define them.  We aren't
  including accuracy from the IEEE definition.  Is that on purpose?}

@@

\begin{defn}
  ``The effort required to learn, operate, prepare input, and interpret output
  of a program'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Once we have verified McCall said this, we can
    remove the VanVliet reference.}
\end{defn}

@@

\begin{defn}
  Effort required to locate and fix an error in a program
  \citep{pressman2005software}. \wss{Peter, if this is from
    McCall, we should just cite the primary source and remove the pressman
    reference.}
\end{defn}

@@

\begin{defn}
  The effort required to locate and fix an error in an operational program
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.) \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.} \wss{PM - can you please look into whether
    \citet{pressman2005software} cite \citet{McCallEtAl1977}?  Do they give a
    reason for dropping the word operational?}  \pmi{Yes,
    \citet{pressman2005software} does cite the relevant section of the textbook
    with \citet{McCallEtAl1977}. While they do not give a reason for
    specifically dropping the word operational, they do indicate that their
    given definition ``is a very limited definition''. Perhaps their intent was
    breadth.} \wss{Peter, please verify the McCall reference definition, and
    then just cite that.  Olu has found the McCall reference, so you shouldn't
    have to search for it.  We can remove both the VanVliet and Pressman
    reference in  preference of the McCall definition.}
\end{defn}

@@

Combined Definition \ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}: The ease with which a software system or
component can be modified to correct faults, improve performance or other
attributes, or satisfy new requirements. \wss{We didn't agree as a group in the
  last meeting on our ``measurement'' term, but I think ease is difficult to
  measure.  Maybe we should rephrase to measuring the effort required?}

@@

\begin{defn} 
  The degree to which a software module or other work product can be used in
  more than one software system \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  Extent to which a program [or parts of a program] can be reused in other
  applications - related to the packaging and scope of the functions that the
  program performs \citep{pressman2005software}. \wss{Peter, if this is from
    McCall, we should just cite the primary source and remove the pressman
    reference.}
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected} 
  The extent to which a software component can be used with or without
  adaptation in a problem solution other than the one for which it was
  originally developed \citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
  Reusability is the likelihood a segment of source code that can be used again
  to add new functionalities with slight or no modification
  \citep{sandhu2010survey}.
\end{defn}

\begin{defn}
  The extent to which a program (or parts thereof) can be reused in other
  applications \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
  \wss{Peter, if this is from McCall, we should just cite the primary source and
    remove the VanVliet reference.}
\end{defn}

@@

\subsection{\notdone{Portability} \pmi{owner}}

@@

\begin{defn} \label{PortabilityDefnSelected} Effort required to transfer the
  program from one hardware and/or software system environment to another
  \citep{pressman2005software}.  \wss{Peter, if this is from McCall, we should
    just cite the primary source and remove the pressman reference.}
\end{defn}

@@

\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Peter, if this is from McCall, we should just
    cite the primary source and remove the VanVliet reference.}
\end{defn}

@@

\pmi{I think this is done.}

@@

\begin{defn}
  ``The effort required to couple one system with another''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)  \wss{Ao, if
    this is from McCall, we should just cite the primary source and remove the
    Van Vliet reference.}
\end{defn}

@@

Thus, we can improve the productivity of the software process by increasing its
outputs, decreasing its inputs, or both. However, this means that we need to
provide meaningful definitions of the inputs and outputs of the software
process.

@@

\begin{defn}
  The degree to which a full implementation of the required functionality has
  been achieved \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
  \wss{Ao, if this is from McCall, we should just cite the primary source and
    remove the Van Vliet reference.}
\end{defn}

@@

\begin{defn}
  The use of uniform design and implementation techniques and notations
  throughout a project \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Ao, if this is from McCall, we should just cite
    the primary source and remove the Van Vliet reference.}
\end{defn}

@@

\begin{defn}
  The ability to link software components to requirements
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn} \wss{Once we have verified McCall, we can remove the Van Vliet
  reference.}

@@

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \citep{VanVliet2000}. \wss{Need to verify McCall reference, then
  delete VanVliet.}

>>>>

\begin{defn} \label{PerformanceDefnSelected}
	The degree to which a system or component accomplishes its designated functions
	within given constraints, such as speed, accuracy, or memory usage
	\citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn} \label{PerformanceDefnSelected2}
	How well or how rapidly the system must perform specific functions. Performance
	requirements encompass speed (database response times, for instance), throughput
	(transactions per second), capacity (concurrent usage loads), and timing (hard
	real-time demands) \citep{wiegers2003softreq}.
\end{defn}
\begin{defn}
	In software engineering we often equate performance with efficiency. A software system is efficient if it uses computing resources economically
	\citep{ghezzi1991fundamentals}.
\end{defn}

@@

Combined definition \ref{PerformanceDefnSelected} and
\ref{PerformanceDefnSelected2}: The degree to which a system or component
accomplishes its designated functions within given constraints, such as speed
(database response times, for instance), throughput (transactions per second),
capacity (concurrent usage loads), and timing (hard real-time
demands). \wss{What is the difference between speed and timing?}

@@

\pmi{I will check if Wiegers discusses the difference between speed and timing.}
\pmi{Wiegers did not discuss this difference.}
\pmi{Speed - change over time; timing - related to specification: when something
	should happen in relation to something else - state transitions}
\wss{If we need both speed and timing, we should define them.  We aren't
  including accuracy from the IEEE definition.  Is that on purpose?}
\pmi{We have decided not to include accuracy. SS will find difference b/w speed and timing from a colleague.}

@@

\begin{defn}
  ``The effort required to learn, operate, prepare input, and interpret output
  of a program'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Once we have verified McCall said this, we can
    remove the VanVliet reference.} \pmi{Yes this is almost exactly from McCall, except he did not have the word "The" at the beginning.}
\end{defn}

@@

@@

\begin{defn}
  Effort required to locate and fix an error in an operational program
  \citep{McCallEtAl1977}. \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.} \wss{PM - can you please look into whether
    \citet{pressman2005software} cite \citet{McCallEtAl1977}?  Do they give a
    reason for dropping the word operational?}  \pmi{Yes,
    \citet{pressman2005software} does cite the relevant section of the textbook
    with \citet{McCallEtAl1977}. While they do not give a reason for
    specifically dropping the word operational, they do indicate that their
    given definition ``is a very limited definition''. Perhaps their intent was
    breadth.} \wss{Peter, please verify the McCall reference definition, and
    then just cite that.  Olu has found the McCall reference, so you shouldn't
    have to search for it.  We can remove both the VanVliet and Pressman
    reference in  preference of the McCall definition.}
\pmi{I have verified the McCall definition and removed the Pressman and van Vliet references above. I will leave these comments until all similar definitions in this document have been edited.}
\end{defn}

@@

Combined altered Definition \ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}: The effort with which a software system or
component can be modified to:

\begin{enumerate}
	\item correct faults
	\item improve performance or other
	attributes
	\item satisfy new requirements
\end{enumerate}

@@

\begin{defn} 
  The degree to which a software module or other work product can be used in
  more than one software system \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  Extent to which a program can be used in other applications - related to the packaging and scope of the functions that programs perform \citep{McCallEtAl1977}. 
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected} 
  The extent to which a software component can be used with or without
  adaptation in a problem solution other than the one for which it was
  originally developed \citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
  Reusability is the likelihood a segment of source code that can be used again
  to add new functionalities with slight or no modification
  \citep{sandhu2010survey}.
\end{defn}

@@

\subsection{{Portability} \pmi{owner}}

@@

\begin{defn} \label{PortabilityDefnSelected} Effort required to transfer a program from one hardware configuration and/or software system environment to another \citep{McCallEtAl1977}.
\end{defn}

@@

@@

@@

\begin{defn}
  ``The effort required to couple one system with another''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)  \wss{Ao, if
    this is from McCall, we should just cite the primary source and remove the
    Van Vliet reference.} \pmi{Yes this is almost exactly from McCall, except he did not have the word "The" at the beginning.}
\end{defn}

@@

Thus, we can improve the productivity of the software process by increasing its
outputs, decreasing its inputs, or both. However, this means that we need to
provide meaningful definitions of the inputs and outputs of the software
process. \wss{Where did this definition come from?  Is this all from Boehm?
  This is quite a long quote.  We might actually want to paraphrase.}

@@

\begin{defn}
  The degree to which a full implementation of the required functionality has
  been achieved \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
  \wss{Ao, if this is from McCall, we should just cite the primary source and
    remove the Van Vliet reference.} \pmi{McCall's definition verbatim: Those attributes of the software that provide full implementation of the functions required.}
\end{defn}

@@

\begin{defn}
  The use of uniform design and implementation techniques and notations
  throughout a project \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Ao, if this is from McCall, we should just cite
    the primary source and remove the Van Vliet reference.} \pmi{McCall's definition verbatim: Those attributes of the software that provide uniform design and implementation techniques and notation.}
\end{defn}

@@

\begin{defn}
  The ability to link software components to requirements
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn} \wss{Once we have verified McCall, we can remove the Van Vliet
  reference.}  \pmi{McCall's definition verbatim: Those attributes of the software that provide a thread from the requirements to the implementation with respect to the specific development and operational environment.}

@@

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \citep{VanVliet2000}. \wss{Need to verify McCall reference, then
  delete VanVliet.} \pmi{McCall's definition verbatim: Effort required to test a program to insure it performs its intended function.}
